\documentclass{amsart}
\usepackage[utf8]{inputenc}

\usepackage{mymacros, stmaryrd, tikz, pstricks, pst-node, pst-text, pst-tree, subfigure, epsfig, psfrag}
\usepackage[all]{xy}
\usepackage{float}

\newtheorem{thm}{Theorem}
\newtheorem{cor}[thm]{Corollary}
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}

\theoremstyle{definition}
\newtheorem{defn}[thm]{Definition}
\newtheorem{rmk}[thm]{Remark}
\newtheorem{notn}[thm]{Notation}
\newtheorem{conj}[thm]{Conjecture}
\newtheorem{eg}[thm]{Example}

\title{GLSM for D4}
\date{\today}

\begin{document}

\maketitle

\begin{center} {\em This is based on Ed's visit to the ICTP in January of 2020.} \end{center}

The orbifold corresponding to the Dynkin diagram $D_4$ is given by the group 
\[
\mathbb{B}D_4:= \left\langle \sigma=\left(\begin{array}{cc} i & 0 \\ 0 & -i \end{array} \right), \tau=\left( \begin{array}{cc} 0 & 1 \\ -1 & 0 \end{array} \right) \right\rangle
\]
acting on $\mathbb{A}^2$.
The group $\bB D_4$ has five irreducible representations $\rho_0, \ldots, \rho_4$ whose ranks are $1,1,1,1,2$, respectively. The representation $\rho_0$ is the trivial representation.
Below we express a GIT problem for which the stable quotient stack is $\bX:= [\bA^2/ \bB D_4]$ for one stability parameter and the minimal resolution $Y$ of the associated singularity for another.

We begin by setting up some notation.
We take $Q$ to be the McKay quiver of the action of $\bB D_4$ on $\bA^2$ and $A:= \bfk Q/I$ where $I$ is the corresponding ideal of relations.
We take $P_0, \ldots, P_4$ to be the projective left-modules of $A$ corresponding to the irreducible representations of $\bB D_4$.
Let $T_0, \ldots, T_4$ be vector spaces of dimensions $1,1,1,1,2$, respectively, and $G:= \text{GL}(\oplus T_i)$.
Fix an isomorphism $\bfk \simeq T_0$ once and for all; we will use this tacitly, replacing $T_0$ by $\bfk$ at times.
We write $L_4:= \det T_4$ and use $I^\dagger$ for the natural isomorphism $I^\dagger \colon T_4^\vee \otimes L_4 \rightarrow T_4$.

\section{The fields and constraints}

The GIT problem is given by the action of $G$ on the fields given below up to some constraints.
The fields are:
\begin{align}
&\bfk \simeq T_0 \\
\bfx \colon &T_0 \longrightarrow T_4 \label{fd:x} \\
\alpha \colon &T_1 \otimes T_1 \longrightarrow L_4 \label{fd:alpha} \\
\beta \colon &T_2 \otimes T_2 \longrightarrow L_4 \label{fd:beta} \\
\gamma \colon &T_3 \otimes T_3 \longrightarrow L_4 \label{fd:gamma} \\
\delta \colon &L_4 \otimes L_4 \longrightarrow T_1 \otimes T_2 \otimes T_3 \label{fd:delta} \\
P \colon &S^2(T_4) \longrightarrow T_1 \label{fd:P} \\ 
Q \colon &S^2(T_4) \longrightarrow T_2 \label{fd:Q} \\
R \colon &S^2(T_4) \longrightarrow T_3. \label{fd:R}
\end{align}

To express the constraints we need more notation.
Note that the field $P$, given in (\ref{fd:P}), maybe naturally rewritten as $P \colon T_4 \rightarrow T_4^\vee \otimes T_1$.
Composing with $I^\dagger$ and tensoring by an appropriate line bundles we get a morphism $$P^\dagger:= I^\dagger \circ P \colon T_4 \otimes L_4 \rightarrow T_4 \otimes T_1.$$
The fact that $P$ factors through the symmetric part $S^2(T_4)$ translates to tracelessness of $P^\dagger$.
We similarly define the morphisms $Q^\dagger$ and $R^\dagger$.

We may compose the fields $P^\dagger,Q^\dagger$ and $R^\dagger$ to express the constraints, they
are:
\begin{align}
    Q^\dagger R^\dagger &= R^\dagger Q^\dagger = \alpha \delta P^\dagger \label{con:qr} \\
    R^\dagger P^\dagger &= P^\dagger R^\dagger = \beta \delta Q^\dagger \label{con:rp} \\
    P^\dagger Q^\dagger &= Q^\dagger P^\dagger = \gamma \delta R^\dagger \label{con:pq} \\
    P^\dagger Q^\dagger R^\dagger &= \alpha \beta \gamma \delta^3 \text{Id}_{T_4} \label{con:pqr} \\
    \det P^\dagger &= \beta \gamma \delta^2 \\
    \det Q^\dagger &= \gamma \alpha \delta^2 \\
    \det R^\dagger &= \alpha \beta \delta^2.
\end{align}
We note that some of the constraints here are superfluous, like the determinant conditions for example; they are stated for convenience.

Fields satisfying the constraints gauged by $G$ above give us a quotient stack $\cM$.

\section{Tannakian duality}

Formally inverting the fields $\alpha, \ldots, R$ in (\ref{fd:alpha})-(\ref{fd:R}) gives a quotient stack $\widetilde{\cM}$ with an open embedding $\widetilde{\cM} \hookrightarrow \cM$.

\begin{proposition}\label{prop:tannaka}
The stack $\widetilde{\cM}$ is isomorphic to $\bX$.
\end{proposition}

\begin{proof}
To simplify notation we pick bases of $T_0, \ldots, T_4$, think of the fields as matrices and let $G$ act by change of basis. 
One may gauge the scalar fields $\alpha, \ldots, \delta$ to $1$.
The subgroup of $G$ fixing the scalar fields at $1$ is $$\{(1,\lambda_1, \ldots, \lambda_4) \in G \,|\, \lambda_1^2=1, \lambda_2^2=1, \lambda_3 = \lambda_1\lambda_2, \det\lambda_4=1\} \subset G.$$

The field $P^\dagger$ is traceless and invertible so we may conjugate it to $\text{diag}(a, -a)$ for some $a \neq 0$.
We also have that $P^\dagger Q^\dagger$ is traceless which implies that $Q^\dagger$ is of the form $\sigma \cdot \text{diag}(b,c)$ where $b,c \neq 0$ and $\sigma$ is the nontrivial $2\times2$ permutation matrix.
The subgroup of the $\SL(4)$ component fixing $P^\dagger$ and $Q^\dagger$ up to scalar is now precisely $\bB D_4$ as presented above.
A careful calculation of how the scalars in $G$ interact with $\bB D_4 \subset \SL(T_4)$ reveals that they act as the rank 1 irreducible representations of $\bB D_4$.
\end{proof}

\begin{corollary}
Take $\phi$ to be the character of $G$ with the weights $(5, -1,\ldots, -1)$ then $\cM^\phi \simeq \bX$
\end{corollary}

\begin{proof}
The determinant of any semi-invariants with weight $n \phi$, with $n>0$, must contain the scalar field $\alpha \beta \gamma \delta$ as a factor.
Therefore $\alpha \beta \gamma \delta \neq 0$ for any $\phi$-stable point of $\cM$ which implies that $\alpha, \ldots, R$ are invertible.  
\end{proof}

\section{The minimal resolution}

Let $\theta$ denote the character of $G$ with weights $(-5,1,\ldots,1)$ and $\cM^\theta$ denote the corresponding GIT quotient.
Furthermore, let $\cN^\theta$ to denote the moduli space of quiver representations of the McKay quiver with stability parameter $\theta$.
Note that $\cN^\theta$ is isomorphic to the minimal resolution $Y$.
We construct morphisms $f \colon \cN^\theta \rightarrow \cM^\theta$ and $g \colon \cM^\theta \rightarrow \cN^\theta$ and show that they are mutual inverses.

\subsection{The morphism $f \colon \cN^\theta \rightarrow \cM$}

Take a family of quiver representations $\cN^\theta(S)$ over a test scheme $S$.
Abusing notation, this gives vector bundles $T_0, \ldots, T_4$ over $S$ of the correct rank, as well as sections corresponding to the paths in the quiver.
We give the morphism $f$ by defining fields over $S$ of our GIT problem from this data.

\subsubsection{The field \bfx}

The arrow from vertex $0$ to vertex $4$ gives us a tautological section $T_0 \rightarrow T_4$ we take that to be the $\bfx$ of (\ref{fd:x}).

\subsubsection{The fields $\alpha, \beta, \gamma$}

Since our family is $\theta$-stable the universal section $T_4 \rightarrow T_1$ corresponding to the arrow $4 \rightarrow 1$ is surjective; its kernel is the line bundle $T_1^\vee \otimes L_4$.
The relations of the McKay quiver imply that the section corresponding to the path $1 \rightarrow 4 \rightarrow 1$ is zero and hence that the following is a complex of universal sections:
$$T_1 \rightarrow T_4 \rightarrow T_1 \rightarrow 0.$$
This gives us a section $T_1 \rightarrow T_1^\vee \otimes L_4$, in other words a morphism $T_1 \otimes T_1 \rightarrow L_4$ that we set to be $\alpha$ of (\ref{fd:alpha}).
We can pick the sections $\beta$ and $\gamma$ of (\ref{fd:beta}) and (\ref{fd:gamma}) in a similar fashion.

\subsubsection{The fields $P, Q, R$}

The construction of $P,Q$ and $R$ is more delicate.
The representations \underline{Hom}$(\rho_0, \rho_4)$ and \underline{Hom}$(\rho_4, \rho_1)$ are isomorphic.
This, in turn, gives us an isomorphism of corresponding projective modules of our quiver and further an isomorphism of vector spaces $\Hom(P_0, P_4) \simeq \Hom(P_4, P_1)$.
We may scale this isomorphism so that it takes the arrow $0 \rightarrow 4$ to the arrow $4 \rightarrow 1$.
Now consider the composite $$T_0 \otimes_\bfk \Hom(P_0, P_4) \rightarrow T_0 \otimes_\bfk \Hom(P_4, P_1) \rightarrow T_4^\vee \otimes T_1$$ where the second factor is the evaluation map.
The stability condition $\theta$ implies $\text{ev} \colon T_0 \otimes_\bfk \Hom(P_0, P_4) \rightarrow T_4$ is surjective; checking that the kernel of ev is zero under the composite above gives us a morphism $T_4 \rightarrow T_4^\vee \otimes T_1$ that we will call $P$. 
The fields $Q$ and $R$ are constructed similarly.

\subsubsection{The constraints and the field $\delta$}

The space $\cM^\theta$ is birational to $\bX$ were the constraints hold: they hold on $\bX$ since the corresponding statements are true for representations of $\bB D_4$.

We therefore have, cf.\ (\ref{con:qr}), that the section $Q^\dagger R^\dagger$ differs from $P^\dagger$ by a constant on all of $\cN^\theta$ while $P^\dagger$ is nonzero.
Similar statements hold for $R^\dagger P^\dagger$ and $P^\dagger Q^\dagger$.
Stability of our family implies that $(\alpha, \beta, \gamma) \neq 0$, we may therefore read off the field $\delta$ from Equations~(\ref{con:qr}), (\ref{con:rp}), (\ref{con:pq}). 
This can probably be said in a clearer fashion using complexes and quasi-isomorphisms but it will do for now.

\subsection{The morphism $g \colon \cM \rightarrow \cN$}

Given an $S$-point of $\cM$, we give the morphism $g$ by defining a family of quiver representations of $Q$ over $S$ and checking that the relations are satisfied.
As before, an $S$-point of $\cM$ naturally gives vector bundles $T_0, \ldots, T_4$ over $S$ of the correct ranks.
It remains to define the sections corresponding to the arrows.

\subsubsection{The arrow $0 \rightarrow 4$}

For this we take the field $\bfx$.

\subsubsection{The arrow $4 \rightarrow 0$}
This is given by the composite
$$T_4 \xrightarrow{\text{id}\otimes u} T_4 \otimes T_4 \rightarrow L_4 \xrightarrow{\alpha\beta\gamma\delta^2} T_0.$$

\subsubsection{The other arrows $4 \rightarrow i$}
We construct this section for $i=1$, the others are similar.
The section corresponding to $1 \rightarrow 4$ is the following composite $$T_4 \xrightarrow{\text{id}\otimes u} T_4 \otimes T_4 \rightarrow S^2(T_4) \xrightarrow{P} T_1.$$

\subsubsection{The other arrows $i \rightarrow 4$}
Tensoring this section $T_4 \rightarrow T_1$ by $\alpha$ we get $T_4 \rightarrow T_1^\vee \otimes L_4$ this naturally gives a section $T_1 \rightarrow T_4^\vee \otimes L_4$, composing with $I^\dagger$ gives the desired section.

\subsubsection{The relations}

The above gives us a homomorphism of algebras \begin{equation} \label{eq:kq1}
    \bfk Q \rightarrow \End_{\cM}(\oplus T_i).
\end{equation}
Proposition~\ref{prop:tannaka} gives an open embedding $\bX \hookrightarrow \cM$ through which pullback gives a monomorphism \begin{equation}\label{eq:kq2}
    \End_{\cM}(\oplus T_i) \hookrightarrow \End_{\bX}(\oplus T_i) \simeq A.
\end{equation}
The composite of the morphisms in (\ref{eq:kq1}) and (\ref{eq:kq2}) is a surjective epimorphism.
Putting these facts together we may conclude that $\End_{\cM}(\oplus T_i) \simeq A$.
That is, our homomorphism $\bfk Q \rightarrow \End_{\cM}(\oplus T_i)$ factors through $A$ and that our fields give sections that satisfy the relations of the quiver.

\subsection{The composite $g \circ f \colon \cN^\theta \rightarrow \cM \rightarrow \cN$ is the open inclusion $\cN^\theta \subset \cN$}

It suffices to check this on the sections corresponding to each arrow.

\subsubsection{The arrow $0 \rightarrow 4$}
This is straight forward.

\subsubsection{The other arrows $4 \rightarrow i$}
We deal with case $i=1$ only; $i=2,3$ are similar.
Let $\bfe_\bfx \colon T_0 \rightarrow  T_0 \otimes \Hom(P_0, P_4)$ be the identity on the component corresponding to the arrow $0 \rightarrow 4$ and 0 elsewhere.
We then have the following commutative diagram:
\begin{equation}
    \xymatrix{T_0 \ar[r]^{\text{id}} \ar[d]^{\bfe_\bfx} & T_0 \ar[d]^\bfx \\
    T_0 \otimes \Hom(P_0, P_4) \ar[r]^-{\text{ev}} \ar[d]^P & T_4 \ar[d]^P \\
    T_0 \otimes \Hom(P_4, P_1) \ar[r]^-{\text{ev}} &T_4^\vee \otimes T_1.
    }
\end{equation}
Note that the field $P$ in the image is defined using the bottom half of the diagram.
The diagram combined with the fact that $P \colon \Hom(P_0, P_4) \rightarrow \Hom(P_4, P_1)$ takes $0 \rightarrow 4$ to $4 \rightarrow 1$ gives us that the section corresponding to $i \rightarrow 4$ gets mapped to itself under $g \circ f$.

\subsubsection{The arrows $i \rightarrow 4$}

For $i =1$, we may naturally rewrite the section corresponding the arrow $4 \rightarrow 1$ as a morphism $T_1^\vee \otimes L_4 \rightarrow T_4$ and fits into the short exact sequence in the diagram below:
\begin{equation}
    \xymatrix{ & T_1 \ar[r] \ar[d]^\alpha & 0 \ar[d] & \\
    0 \ar[r] & T_1^\vee \otimes L_4 \ar[r] & T_4 \ar[r] & T_1 \ar[r] & 0.} 
\end{equation}
Now since the field $\alpha$ in the image is given by the non-trivial vertical arrow we have the result for $i=1$.
The cases $i=2,3$ are similar.
The case $i=0$ follows from the relations of the quiver.

\subsection{Stability and conclusion}

We begin with the morphism $f$.
The $\theta$-stability of a family of points of $\cN$ gives non-vanishing sections of the bundles $T_1, \ldots, T_3$ and a surjective morphism $T_0^{\oplus 2} \rightarrow T_4$.
These give rise to analogous sections and morphisms on $\cM$; they remain non-zero and surjective on $\cM$, since the composite $g \circ f$ is an open inclusion, and therefore give rise to non-vanishing $\theta$-semi-invariant on $\cM$.

We now have a pair of birational morphisms $f \colon \cN^\theta \rightarrow \cM^\theta$ and $g \colon \cM^\theta \rightarrow \cN^\theta$ for which $g \circ f$ is the identity hence they are isomorphisms.


%
%\section{Earlier correspondence}
%
%We begin by introducing the GIT problem without much context just in case you came across something similar before.
%We then hand-wave a little to explain the motivation behind this.
%
%The orbifold corresponding to the Dynkin diagram $D_4$ is given by the group 
%\[
%\mathbb{B}D_4:= \left\langle \sigma=\left(\begin{array}{cc} i & 0 \\ 0 & -i \end{array} \right), \tau=\left( \begin{array}{cc} 0 & 1 \\ -1 & 0 \end{array} \right) \right\rangle
%\]
%acting on $\mathbb{C}^2$. 
%The moduli space of $\theta$-stable quiver representation on the McKay quiver for any generic stability parameter $\theta$ will be denoted $\cM^\theta$.
%We have that $\cM^\theta$ is isomorphic to the minimal resolution $Y$ of the corresponding singularity for any generic stability parameter $\theta$.
%
%Take $T_1, \ldots, T_6$ to be vector spaces with dimension vector $(1,1,1,2,2,2)$.
%Also impose the following restriction on the choice of vector spaces above.
%In what follows $\text{det}$ is the top exterior power.
%\begin{align*}
%    \text{det}(T_5) &= T_1 \otimes T_2 \otimes T_3 \\
%    \text{det}(T_6) &= \text{det}(T_4) \otimes T_1 \otimes T_2 \otimes T_3.
%\end{align*}
%
%The vector spaces $T_1, \ldots, T_4$ should be thought of as the fibres of the universal bundle over $\cM^\theta$ for some fixed $\theta$ (we take $T_0$ to be the $\bfk$).
%In other words, the first chern classes of each these bundles are dual to the classes of the irreducible components in the exceptional locus of $Y$.
%The spaces $T_5$ and $T_6$ are the fibres of rank two universal bundle arising from different choices of quiver stability parameters, up to tensoring by a universal line bundle.
%Up to tensoring by a line bundle, $T_4$, $T_5$ and $T_6$ are the only rank two vector bundles on $Y$ arising as universal bundles on the $\cM^\theta$ for any generic quiver stability parameter.
%For general $D_n$ the number of such rank two bundles is $2^{n-1}-n-1$.
%
%For a reason that is not yet clear to me, the building blocks of the GIT problem that relate $Y$ to the stack $[\mathbb{C}^2/G]$ are the following fields:
%\begin{align*}
%&\bfk \longrightarrow T_4 \\
%A \colon &T_5 \otimes T_1 \longrightarrow T_6 \\
%B \colon &T_5 \otimes T_2 \longrightarrow T_6 \\
%C \colon &T_5 \otimes T_3 \longrightarrow T_6 \\
%M \colon &T_4 \otimes \text{det}(T_4) \longrightarrow T_6
%\end{align*}
%The morphisms $A$, $B$ and $C$ are required to satisfy the condition that $AB^{-1}$, $BC^{-1}$ and $CA^{-1}$ are traceless.
%In particular, this is not really `linear'.
%This condition of $A$, $B$, and $C$ comes from the mutual-commutativity of the corresponding elements $s_1$, $s_2$ and $s_3$ in the braid group.
%
%Our gauge group is $$G := \{(g_1, \ldots,g_6) \in (\times_i \text{GL}(T_i)) \, |\, \text{det}(g_5)= g_1 g_2 g_3 \, , \,\, \text{det}(g_6)= \text{det}(g_4)g_1 g_2 g_3 \}.$$
%
%We now show that we get the corresponding orbifold if we insist $A,B,C$ and $M$ are isomorphisms.
%We may act by the element $$(1, \det M, 1, M, (\det A^{-1}\cdot \det M)^{\frac{1}{2}} \cdot A, \det M \cdot \text{Id}) \in G$$ to fix $M=\text{Id}$ and $A= \mu_1 \cdot \text{Id}$ for some scalar $\mu_1$. Therefore, we may assume $M = \text{Id}$ and $A = \mu_1 \cdot \text{Id}$.
%The subgroup of $G$ fixing $M= \text{Id}$ and $A= \mu_1 \cdot \text{Id}$ is given by elements of the form $$(g_1, g_2, g_3, g_4, (g_1 g_2 g_3 \det g_4^{-1})^\frac{1}{2} \cdot g_4, (g_1g_2g_3)^\frac{1}{2} \cdot g_4) \in G$$
%
%The tracelessness of $BA^{-1}$ and $CA^{-1}$ then implies that both $B$ and $C$ are traceless. We may act on $B$ by change of basis while preserving the fact that $M$ is the identity and $A$ is a scalar matrix. We may therefore assume that $B$ is of the form 
%$$\begin{pmatrix}
%\mu_2 & 0 \\
%0 & - \mu_2
%\end{pmatrix}.$$
%Tracelness of $BC^{-1}$ then forces $C$ to be of the form 
%$$\begin{pmatrix}
%0 & \mu_3 \\
%\mu_3 & 0
%\end{pmatrix}.$$
%To fix $\mu_1 = \mu_2 = \mu_3 = 1$ we act by $$(\mu_1, \mu_2, \mu_3, \text{Id}, (\mu_1\mu_2\mu_3)^\frac{1}{2}\cdot \text{Id}, (\mu_1\mu_2\mu_3)^\frac{1}{2}\cdot \text{Id}) \in G.$$ 
%The result then follows from Tannakian duality.
%
%\begin{rmk}
%From this data we may construct a morphism $T_4 \otimes T_4 \rightarrow T_1$. First note that such a morphism is equivalent to a morphism $T_4 \rightarrow T_4^\vee \otimes T_1$. Invoking the natural isomorphism $T_4^\vee \cong T_4 \otimes \det(T_4)^\vee$, this is equivalent to a morphism $\det(T_4) \otimes T_4 \rightarrow T_4 \otimes T_1$.
%
%Further applications of the natural isomorphism $V^\vee \cong V \otimes \det(V)^\vee$, gives us morphisms:
%\begin{align*}
%A^{T} &\colon T_6 \otimes T_1 \longrightarrow T_5 \otimes \det(T_4) \\
%B^{T} &\colon T_6 \otimes T_2 \longrightarrow T_5 \otimes \det(T_4) \\
%C^{T} &\colon T_6 \otimes T_3 \longrightarrow T_5 \otimes \det(T_4) \\
%M^{T} &\colon T_6 \otimes \det(T_4) \longrightarrow T_4 \otimes T_1 \otimes T_2 \otimes T_3.
%\end{align*}
%
%Now the morphism $\det(T_4) \otimes T_4 \rightarrow T_4 \otimes T_1$ is given by the composite $MC^{T}BM$ (or equivalently $MB^{T}CM$): $$\det(T_4) \otimes T_4 \rightarrow T_6 \rightarrow T_5 \otimes \det(T_4) \otimes T_3^\vee \rightarrow T_6 \otimes \det(T_4) \otimes T_2^\vee \otimes T_3^\vee \rightarrow T_4 \otimes T_1.$$
%\end{rmk}
%
%\begin{rmk}
%Note that one may reconstruct a representation of the McKay quiver equipped with this data along with a morphism $T_0 \rightarrow T_4$. Take, for example the arrow $T_4 \rightarrow T_1$, this is given by the composite $$T_4 \rightarrow T_4 \otimes T_4 \rightarrow T_1.$$
%\end{rmk}
%
%\begin{rmk}
%Tracelessness of $AB^{-1}$ (and the like) follows from the need for  the equality $AB^{T}= \lambda BA^{T}$ for some scalar $\lambda$. That is, the morphisms $AB^{T}$ and $BA^{T}$ differ by tensoring by a line bundle. This comes from the braid relations.
%\end{rmk}
%
%\subsection*{Where does this come from?}
%
%Any GLSM that recovers the orbifold should contain enough data to recover the stabiliser group at the origin. 
%Tannakian philosophy implies that one should try to capture the monoidal data of the category of representations to achieve this result.
%
%Our group $\bB D_4$ has four non-trivial irreducible representations: three of dimension 1 and a two dimensional one. We abuse notation by using the same letters $T_i$ to denote both the irreducile representations of $\bB D_4$ and the universal bundels on the corresponding McKay quiver.
%We have that the monoidal structure is given by the following isomorphisms:
%\begin{align*}
%\text{ for } i \in \{1,2,3\} \quad T_i \otimes T_i &\rightarrow \det T_4 \\
%\text{ for } \{i,j,k\} = \{1,2,3\} \quad T_i \otimes T_j &\rightarrow T_k\\
%\det T_4  &\rightarrow T_0 \\
%\text{S}^2(T_4) &\rightarrow T_1 \oplus T_2 \oplus T_3.
%\end{align*}
%
%We fix a generic stability parameter $\theta$ and $T_1, \ldots T_4$ be the universal bundles on $\cM^\theta$.
%We look for generic stability parameter $\theta'$ for which the universal bundles are given by $(T_1 \otimes T_i), \ldots, (T_4 \otimes T_i)$ for $i = 1,2,3$ or $(T_1 \otimes \det T_4), \ldots, (T_4 \otimes \det T_4)$.
%We then compute the element in the braid group taking the chamber containing $\theta$ to that containing $\theta'$.
%This gives us a series of spherical twists each of which changes exactly one universal bundle.
%The spherical twists also give us a morphism between the bundles across the corresponding hyperplanes.
%The morphisms $A$, $B$, $C$ and $D$ above are such morphisms.
%They correspond to the spherical twists corresponding to the simples at $1$, $2$, $3$ and $4$ respectively.
\end{document}
